### 2022-11-15 NSF2022/Description/summary.tex
yny 1114f

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of granules. The main
ingredient is a nonlocal interaction through the solution of an moving
domain elliptic PDE that encompasses long-range amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-known vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
amphiphilic ensembles, improving on mathematical models, efficient,
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory for the collective dynamics.

>>>>

\subsection*{Intellectual Merit}
\vspace{-0.1in}
This collaborative project focuses on modeling, simulation, and analysis
of self-assembly and collective dynamics of a suspension of granules with 
non-uniform hydrophobicity on their boundaries. The main
ingredient is a nonlocal interaction through the solution of moving
domain elliptic PDEs that encompasses long-range (non-additive) amphiphilic and
short-range steric interactions. The PIs have validated this
coarse-grained model against well-studied vesicle hydrodynamics. The
technical research tasks include quantifying collective properties of
ensembles of granules with tunable hydrophobicity, analyzing the mathematical model in 
distinguished limits to make connection with continuum models,
designing efficient and
high-order numerical algorithms for large-scale two- and
three-dimensional simulations with confinement, and developing a kinetic
theory to quantify the both the polar and nematic characteristics in the collective dynamics.
